The \dealii{} Library, Version 9.2

### 2020-06-10 9.2/paper.tex
Discuss the new code gallery examples.

\todo[inline]{Do we have new code gallery programs?}
\begin{itemize}
  \item Parallel in time (\url{https://github.com/dealii/code-gallery/pull/49})
  \item Linear elastoplasticity (\url{https://github.com/dealii/code-gallery/pull/62})
  \item Thermo-electro-elastic pump (\url{https://github.com/dealii/code-gallery/pull/63})
  \item Nonlinear poro-viscoelasticity (\url{https://github.com/dealii/code-gallery/pull/72})
\end{itemize}

@@

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
%
% Uwe Koecher doesn't usually show up in the changelog, but
% we should make sure he's listed.
%
% 9.2: updated 5/11/2020 MM
Pasquale Africa,
Ashna Aggarwal,
Giovanni Alzetta,
Mathias Anselmann,
Kirana Bergstrom,
Manaswinee Bezbaruah,
Benjamin Brands,
Yong-Yong Cai,
Fabian Castelli,
Katherine Cosburn,
Denis Davydov,
Elias Dejene,
Stefano Dominici,
Brett Dong,
Luel Emishaw,
Niklas Fehn,
Rebecca Fildes,
Menno Fraters,
Andres Galindo,
Daniel Garcia-Sanchez,
Rene Gassmoeller,
Melanie Gerault,
Nicola Giuliani,
Brandon Gleeson,
Anne Glerum,
Krishnakumar Gopalakrishnan,
Graham Harper,
Mohammed Hassan,
Nicole Hayes,
Bang He,
Johannes Heinz,
Jiuhua Hu,
Lise-Marie Imbert-Gerard,
Manu Jayadharan,
Daniel Jodlbauer,
Marie Kajan,
Guido Kanschat,
Alexander Knieps,
Uwe K{\"o}cher,
Paras Kumar,
Konstantin Ladutenko,
Charu Lata,
Adam Lee,
Wenyu Lei,
Katrin Mang,
Mae Markowski,
Franco Milicchio,
Adriana Morales Miranda,
Bob Myhill,
Emily Novak,
Omotayo Omosebi,
Alexey Ozeritskiy,
Rebecca Pereira,
Geneva Porter,
Laura Prieto Saavedra,
Roland Richter,
Jonathan Robey,
Irabiel Romero,
Matthew Russell,
Tonatiuh Sanchez-Vizuet,
Natasha S. Sharma,
Doug Shi-Dong,
Konrad Simon,
Stephanie Sparks,
Sebastian Stark,
Simon Sticko,
Jan Philipp Thiele,
Jihuan Tian,
Sara Tro,
Ferdinand Vanmaele,
Michal Wichrowski,
Julius Witte,
Winnifried Wollner,
Ming Yang,
Mario Zepeda Aguilar,
Wenjuan Zhang,
Victor Zheng.

@@

Clemson University is acknowledged for generous allotment of compute time on
Palmetto cluster.

>>>>

There are also new programs in the code gallery (a collection of
user-contributed programs that often solve more complicated problems
than tutorial programs, and intended as starting points for further
research rather than as teaching tools):
\begin{itemize}
  \item A program based on the XBraids library to solve time-dependent
    problems in a parallel-in-time fashion. This program was
    contributed by Joshua Christopher.
  \item A program that solves the biphasic nonlinear
    poro-viscoelasticity equations based on Ogden hyperelasticity, to
    explore the porous and viscous contributions in brain mechanics
    applications.  This program was contributed by Ester Comellas and
    Jean-Paul Pelteret. The program also serves as a demonstration of
    the automatic differentiation capabilities of \dealii{}.
\end{itemize}

@@

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
%
% Uwe Koecher doesn't usually show up in the changelog, but
% we should make sure he's listed.
%
% 9.2: updated 5/11/2020 MM
Pasquale Africa,
Ashna Aggarwal,
Giovanni Alzetta,
Mathias Anselmann,
Kirana Bergstrom,
Manaswinee Bezbaruah,
Benjamin Brands,
Yong-Yong Cai,
Fabian Castelli,
Joshua Christopher,
Ester Comellas,
Katherine Cosburn,
Denis Davydov,
Elias Dejene,
Stefano Dominici,
Brett Dong,
Luel Emishaw,
Niklas Fehn,
Rebecca Fildes,
Menno Fraters,
Andres Galindo,
Daniel Garcia-Sanchez,
Rene Gassmoeller,
Melanie Gerault,
Nicola Giuliani,
Brandon Gleeson,
Anne Glerum,
Krishnakumar Gopalakrishnan,
Graham Harper,
Mohammed Hassan,
Nicole Hayes,
Bang He,
Johannes Heinz,
Jiuhua Hu,
Lise-Marie Imbert-Gerard,
Manu Jayadharan,
Daniel Jodlbauer,
Marie Kajan,
Guido Kanschat,
Alexander Knieps,
Uwe K{\"o}cher,
Paras Kumar,
Konstantin Ladutenko,
Charu Lata,
Adam Lee,
Wenyu Lei,
Katrin Mang,
Mae Markowski,
Franco Milicchio,
Adriana Morales Miranda,
Bob Myhill,
Emily Novak,
Omotayo Omosebi,
Alexey Ozeritskiy,
Rebecca Pereira,
Geneva Porter,
Laura Prieto Saavedra,
Roland Richter,
Jonathan Robey,
Irabiel Romero,
Matthew Russell,
Tonatiuh Sanchez-Vizuet,
Natasha S. Sharma,
Doug Shi-Dong,
Konrad Simon,
Stephanie Sparks,
Sebastian Stark,
Simon Sticko,
Jan Philipp Thiele,
Jihuan Tian,
Sara Tro,
Ferdinand Vanmaele,
Michal Wichrowski,
Julius Witte,
Winnifried Wollner,
Ming Yang,
Mario Zepeda Aguilar,
Wenjuan Zhang,
Victor Zheng.

@@

Clemson University is acknowledged for generous allotment of compute time on
the Palmetto cluster.
